---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pwrcontour

<!-- badges: start -->
<!-- badges: end -->

The goal of pwrcontour is to present power analyses in which it is
possible to evaluate power for numerous hypothetical effect sizes at
once. This makes it easier to communicate the fact that power is a
calibration for different potential contingencies of the true size of
the effect of interest. This is based on the tables and figures created
by Richard Morey in the jamovi jpower module.

This package is still in alpha, and more features will likely be added
at a later point.

## Installation

You can install the released version of pwrcontour from Github with:

``` r
remotes::install_github("mathesong/pwrcontour")
```

## Example

The main functions are simply for plotting power contours, or examining
power tables, based around the syntax of the functions in the `pwr`
package.

### Correlations

```{r example_r}
library(pwrcontour)

pwr.r.test.contour(nmin = 5, nmax = 100, rmin = 0.1, rmax = 0.7)
pwr.r.test.table(n = 25)
```

### T-tests

```{r example_t}
pwr.t.test.contour(nmin = 5, nmax = 100, esmin = 0.1, esmax = 1)
pwr.t.test.table(n = 25)
```

This package also makes it possible to present these figures in the raw units of analysis. For example, if we know that a 10% change is equivalent to a Cohen's d of 1, we can incorporate this into the figure.


```{r example_t2}
pwr.t.test.contour(nmin = 5, nmax = 100, esmin = 1, esmax = 10, 
                   d_unitconversion = 10, d_units = "%")
pwr.t.test.table(25, d_unitconversion = 10, d_units = "%")
```


### Proportion tests


Then there's also proportion tests. I decided to discard the Cohen's h, as this feels like it complicates things unnecessarily. So we set up a proportion to compare to instead, called `propcomp`

```{r example_prop}
pwr.prop.test.contour(nmin = 5, nmax = 100, propmin = 0.01, propmax = 0.99, 
                      propcomp = 0.75)
pwr.prop.test.table(n=75, propcomp=0.75)
```

